Make any stupid plot you want

### 2021-01-18 draft/sections/math.tex
new pdf

We use fiber bundles\cite{FiberBundle2020, rowlandFiberBundle} to model data and graphics because they allow us to seperate the variables in a dataset from how the values  are connected to each other. The fiber bundles mentioned in this work are assumed to be locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}.

@@

\subsection{Data Space}
\label{sec:data}
Generally when we discuss data, we are interested in two aspects: the variables in the dataset

% introduce what this is gonna happen in this section - we will talk about, fiber and connectivity 
% motivate w/ data/ example - have weather station. %tidydata 
% we will introduce the fiber bundle and its components base and total space to explain the fiber

As proposed by Butler \cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}

@@

\subsubsection{Data: Section}
%%% visual variable encoding in a consistent/atomic way in a complex structure 
\label{sec:section_data}
The sections of the fiber bundles are the instances of the data. They are the functions that map from a point $k \in K$ to a set of values in $F$. For example, if we have a database, the section is the table that yields a row given an index. The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}

@@

\subsubsection{Sheaf and Stalk}
\label{sec:sheaf_stalk}
%%% sheaf is how we break up the base space 
Often a graphic may need to be updated with live data or support zooming in on a segement of the dataset; to support working with a subset of data, we can use the sheaf $\mathcal{O}(E)$

>>>>

We use fiber bundles\cite{FiberBundle2020, rowlandFiberBundle} to model data and graphics because they allow us to seperate the variables in a dataset from how the values  are connected to each other \cite{butlerVisualizationModelBased1989,butlerVectorBundleClassesForm1992}. The fiber bundles mentioned in this work are assumed to be locally trivial\cite{spanier1989algebraic,LocallyTrivialFibre}.

@@

\subsection{Data Space}
\label{sec:data}
Lets say we are working with the Global Historical Climatology Network\cite{AnOverviewoftheGlobalHistoricalClimatologyNetworkDailyDatabase}, which is a global daily record of weather station  such as rainfall and temperature. Depending on which aspects of the data we want to visualize, we can encode it as a timeseries or map or both or even represent the measurements as completely disconnected.

Using a fiber bundle allows us to encode the properties of the heterogenous variables (\ref{sec:data_fiber}), the connectivity of the measurements (\ref{sec:data_base}), and functions between these spaces that yield the measurements (\ref{sec:data_section}).

@@

\subsubsection{Data: Section}
\label{sec:data_section}
%%% visual variable encoding in a consistent/atomic way in a complex structure 
\label{sec:section_data}
The sections of the fiber bundles are the instances of the data. They are the functions that map from a point $k \in K$ to a set of values in $F$. For example, if we have a database, the section is the table that yields a row given an index. The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}

@@

\subsubsection{Sheaf and Stalk}
\label{sec:data_sheaf_stalk}
%%% sheaf is how we break up the base space 
Often a graphic may need to be updated with live data or support zooming in on a segement of the dataset; to support working with a subset of data, we can use the sheaf $\mathcal{O}(E)$
